Main focus of this report is to analyze, and compare between models, the performance impact of varying vocabulary size for different data types as well as difficulties of distinguishing the eight different topics. The result of the analysis can be seen in Figure \ref{fig:hitratio} \& \ref{fig:confmat} and Table \ref{tab:similarity}.\\\\
Figure \ref{fig:hitratio} shows, for the different models and data types, the overall hit ratio of correct classification as a function of vocabulary size after $\chi^2$ pruning. By comparing the figures it can be noted that the maximum accuracy of 76\% is attained with binary inputs by Multinomial at a vocabulary size of 1022 words. Another observation is that Bernoulli is sensitive to vocabulary size compared to other models and SVM seems in contrast to Bernoulli more robust to changes in vocabulary size. More results derived from these figures are that Random Forest is independent of the feature format and Hybrid follows the behavior of Multinomial.\\\\
The confusion matrices in Figure \ref{fig:confmat} describes the accuracy for specific topics. The rightmost column describes for a certain topic how many articles it contains and the percentage of how correct the model predicted. The bottom row describes for a certain predicted class, how many times that was the target class, and the percentage correct out of them. Analyzing the matrices one can observe that Sport and Education is fairly easy to classify in contrast to Technology and Education which is often misclassified as Science \& Environment and Business respectively. Notable is that Random Forest has a tendency of predicting Sports.\\\\
In Table \ref{tab:similarity} a comparison of the similarity of prediction when mispredicting is shown. The values are resembles, given that both classifiers predicted wrong class, how many times they predicted the same class.
%Table of similarities
\input{sections/result_sub/result_similarity.tex}
\onecolumn
\input{sections/result_sub/result_hitratio.tex}
\onecolumn
\input{sections/result_sub/result_confusion.tex}
\onecolumn
\input{sections/result_sub/result_hitratio_vs_data.tex}
\twocolumn
